A Deep Learning Approach for Gait Event Detection from a Single Shank-Worn IMU: Validation in Healthy and Neurological Cohorts

### 2022-04-22 paper/MDPI_template/article.tex
Edited authors, and submission completed

% Authors, for the paper (add full first names)
\Author{Robbin Romijnders$^{1}$*\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1}$}

@@

% Contact information of the corresponding author
\corres{Correspondence: r.romijnders@neurologie.uni-kiel.de (R.R.)}

@@

\funding{}

>>>>

% Authors, for the paper (add full first names)
\Author{Robbin Romijnders$^{1}$\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1}$*}

@@

% Contact information of the corresponding author
\corres{Correspondence: w.maetzler@neurologie.uni-kiel.de (W.M.)}

@@

\funding{We acknowledge financial support by Land Schleswig-Holstein within the funding programme Open Access Publikationsfonds.}
